Model Search in Relational Domains

### 2016-10-23 experiments.tex
experiment and background proof read

We verified a total of 66 ANSI-C benchmarks, which are derived from (a)~the
bit-vector regression category in SV-COMP'16, (b)~bit-precise and
cycle-accurate software models of hardware circuits automatically generated
using v2c~\cite{mtk2016}, (c)~controller code generated from Simulink
(d)~several hand-crafted benchmarks for equivalence checking and bounded
loop analysis.  All bounded loops are completely unrolled before analysis. 
We compare our tool with the state-of-the-art SAT-based bounded model checker
CBMC (version 5.5)~\cite{cbmc} and a commercial static analysis tool, 
Astr{\'e}e (version 14.10). 
CBMC uses MiniSAT~2.2.1 in the backend.  Astr{\'e}e uses a 
range of abstract domains, which includes interval, 
bit-field, congruence, trace partitioning and relational domains
(octagons, polyhedra, zones, equalities, filter).  ACDCL is instantiated
with a product domain of Booleans and template polyhedra.  We use the
interval and octagon templates for our experiments.  ACDCL is configured
with a heuristic choice of decision (ordered, random, berkmin), propagation
(forward and multi-way) and conflict-analysis (learning UIP, DPLL-style). 
The timeout for our experiments is set to one hour.
%
\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}

@@

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & Decisions & propagations & conflicts & conflict literals & restarts \\ \hline
MiniSat & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\vspace*{-3ex} %BAD TRICK
\end{table}

@@

\paragraph {\textbf{Decision Heuristics}}
%
Figure~\ref{prop-dec}(b) presents a visualisation of the performance of
different decision heuristics in ACDCL.  Note that the runtimes for all
decision heuristics are obtained with multi-way propagation strategy.  The
runtimes are very close, but we observe some key characteristics of these
heuristics.  The Berkmin heuristic performs consistently well for most safe
benchmarks and all bit-vector category benchmarks.  By contrast, the ordered
heuristic performs better for programs with conditional branches since it
prioritises decisions on meet irreducibles that appear in conditional
branches over meet irreducibles that involve numerical variables.  The
runtimes for the random heuristic are marginally higher than for the other
two.  This suggests that domain-specific decision heuristics are important
for ACDCL.

>>>>

We verified a total of 66 ANSI-C benchmarks, which are derived from (a)~the
bit-vector regression category in SV-COMP'16, (b)~bit-precise and
cycle-accurate software models of hardware circuits automatically generated
using v2c~\cite{mtk2016}, (c)~controller code generated from Simulink
(d)~several hand-crafted benchmarks for equivalence checking and bounded
loop analysis.  All bounded loops are completely unrolled before analysis. 
We compare our tool with the state-of-the-art SAT-based bounded model checker
CBMC (version 5.5)~\cite{cbmc} and a commercial static analysis tool, 
Astr{\'e}e (version 14.10)~\cite{astree}. 
CBMC uses MiniSAT~2.2.1 in the backend.  Astr{\'e}e uses a 
range of abstract domains, which includes interval, 
bit-field, congruence, trace partitioning and relational domains
(octagons, polyhedra, zones, equalities, filter).  ACDCL is instantiated
with a product domain of Booleans and template polyhedra.  We use the
interval and octagon templates for our experiments.  ACDCL is configured
with a heuristic choice of decision (ordered, random, berkmin), propagation
(forward and multi-way) and conflict-analysis (learning UIP, DPLL-style). 
The timeout for our experiments is set to one hour.
%
\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}

@@

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & decisions & propagations & conflicts & conflict literals & restarts \\ \hline
MiniSat & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\vspace*{-3ex} %BAD TRICK
\end{table}

@@

\paragraph {\textbf{Decision Heuristics}}
%
Figure~\ref{prop-dec}(b) presents a visualisation of the performance of
different decision heuristics in ACDCL.  Note that the runtimes for all
decision heuristics are obtained with multi-way propagation strategy.  The
runtimes are very close, but we observe some key characteristics of these
heuristics.  The Berkmin heuristic performs consistently well for most safe
benchmarks and all bit-vector category benchmarks.  By contrast, the ordered
heuristic performs better for programs with conditional branches since it
prioritises decisions on meet irreducibles that appear in conditional
branches over meet irreducibles that involve numerical variables.  The
runtimes for the random heuristic are marginally higher than the other
two.  This suggests that domain-specific decision heuristics are important
for ACDCL.
